% !TEX TS-program = xelatex
% !TEX encoding = UTF-8

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% SIMPLE-RESUME-CV
%% <https://github.com/zachscrivena/simple-resume-cv>
%% This is free and unencumbered software released into the
%% public domain; see <http://unlicense.org> for details.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% INSTRUCTIONS FOR COMPILING THIS DOCUMENT ("CV.tex")
%% TEX ---(XeLaTeX)---> PDF:
%%
%% Method 1: Use latexmk for fully automated document generation:
%%   latexmk -xelatex "CV.tex"
%%   (add the -pvc switch to automatically recompile on changes)
%%
%% Method 2: Use XeLaTeX directly:
%%   xelatex "CV.tex"
%%   (run multiple times to resolve cross-references if needed)
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%



\documentclass[a4paper,10pt,oneside]{article}
%\documentclass[letterpaper,10pt,oneside]{article}

% Do not stop on errors during compilation.
\nonstopmode

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% PREAMBLE.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\input{CV-Preamble.tex}
\usepackage{nopageno}
% CV Info (to be customized).
\newcommand{\CVTitle}{Shane Deiley Resume}
\newcommand{\CVNote}{Resume Compiled on May 7}

% PDF settings and properties.
\hypersetup{
pdftitle={\CVTitle},
pdfauthor={Shane Deiley},
pdfsubject={},
pdfcreator={XeLaTeX},
pdfproducer={},
pdfkeywords={},
bookmarks=true,
unicode=true,
bookmarksopen=true,
pdfstartview=FitH,
pdfpagelayout=OneColumn,
pdfpagemode=UseOutlines,
hidelinks,
breaklinks}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% ACTUAL DOCUMENT.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}
\tracingall
%%%%%%%%%%%%%%%
% TITLE BLOCK %
%%%%%%%%%%%%%%%

\title{Shane Deiley}

\begin{subtitle}
7011 W Western Reserve Rd, Canfield, OH 44406
\par
\href{mailto:deileyshane@outlook.com}
{\textbf{deileyshane@outlook.com}}
\,\BulletSymbol\,
\,(330)\,550-9949
\,\BulletSymbol\,
\href{http://www.github.com/sdeiley}
{\textbf{http://www.github.com/sdeiley}}
\end{subtitle}

\begin{body}


%%%%%%%%%%%%%%%
%% Summary   %%
%%%%%%%%%%%%%%%

\section{Objective}
{Objective}
{PDF:Objective}

Lifelong learned and problem solver looking for software engineering opportunities to expand skill set and solve difficult problems with data-driven and analytic solutions.

%%%%%%%%%%%%%%%
%% EDUCATION %%
%%%%%%%%%%%%%%%

\section{Education}
{Education}
{PDF:Education}

\href{http://engineering.wustl.edu/Pages/home.aspx}
{\textbf{Washington University in Saint Louis}},
St. Louis, Missouri, USA
\par
Bachelor of Science Candidate in 
\href{http://cse.wustl.edu/Pages/default.aspx}
{Computer Science}
\hfill
\DatestampYMD{2012}{8}{15} --
\DatestampYMD{2016}{5}{17}
\begin{detail}
Minor in \href{http://wumath.wustl.edu}{Mathematics}
\BulletItem
Cumulative GPA: 3.65 / 4.0
%\BulletItem
%Expected Graduation: May 2016
\BulletItem
Deans List: Fall 2012, Fall 2013, Spring 2014, Spring 2016
\end{detail}

\EntryGap
\textit{Relevant Coursework}
\par
Artificial Intelligence and Machine Learning, Data Mining, Algorithms and Data Structures, Object-oriented Programming, Probability and Statistics, Statistical Modeling, Web Development, and more

%%%%%%%%%%%%%%%%%%%%%%%%%
%% Work EXPERIENCE %%
%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Work Experience}
{Work Experience}
{PDF:WorkExperience}

\href{http://www.microsoft.com/en-us/default.aspx}
{\textbf{Microsoft Corporation}},
Seattle, Washington, USA
\par
Software Development Engineer, OSG
\hfill
\DatestampYMD{2016}{07}{25} -- Present
\begin{detail}
\BulletItem
Description:
SDE in Operating Systems Group.
\BulletItem
Responsibilities:
Various.
\end{detail}

\href{http://www.microsoft.com/en-us/default.aspx}
{\textbf{Microsoft Corporation}},
Seattle, Washington, USA
\par
Software Development Engineering Intern, MPSIT
\hfill
\DatestampYMD{2015}{05}{18} --
\DatestampYMD{2015}{08}{12}
\begin{detail}
\BulletItem
Project:
Data Pipeline Design/Construction and Anomaly Alerting
\BulletItem
Supervisor:
\href{https://www.linkedin.com/pub/kevin-mcclintock/4/590/805}{Kevin McClintock}
\BulletItem
Description:
Utilized various Azure technologies (Sql, Blob Storage, ServiceBus Queue, Cloud Services, Anomaly Detection) to implement a data pipeline for anomaly detection alerting on product signing data.
\BulletItem
Responsibilities:
Create SSIS for ETL process, structure a series of cloud services to retrieve, format, and send data to an anomaly detection api, parse the results, and alert anomalous data.
\end{detail}


%%%%%%%%%%%%%%%%%%%%%%%%%
%% RESEARCH EXPERIENCE %%
%%%%%%%%%%%%%%%%%%%%%%%%%

\section
{Research Experience}
{Research Experience}
{PDF:ResearchExperience}

\href{http://cse.wustl.edu/}
{\textbf{Washington University Department of Computer Science}}
\par
Undergraduate Research Student
\hfill
\DatestampYMD{2015}{08}{25} --
\DatestampYMD{2016}{05}{01} (researh ongoing)
\begin{detail}
\BulletItem
Project:
Guassian Processes for Sorghum Biomass Yield Prediction
\BulletItem
Supervisor:
\href{http://www.cse.wustl.edu/~garnett/}{Dr. Roman Garnett} and Partner: Chip Schaff
\BulletItem
Description:
Implemented and tested gaussian process extensions to the public GPML matlab repository.  Added extensions for multi-task learning.  Using model-generated test data, predictions of growth in multiple weather classified seasons were accurate after just 20 days of training.
\end{detail}

\href{http://reu.cse.wustl.edu/reu/Welcome.html}
{\textbf{Washington University Computer Science Research Experience for Undergraduates}}
\par
Undergraduate Research Student, Computer Science Department
\hfill
\DatestampYMD{2014}{05}{15} --
\DatestampYMD{2014}{12}{20}
\begin{detail}
\BulletItem
Project:
Parallel Data Structures
\BulletItem
Supervisor:
\href{http://www.cse.wustl.edu/~kunal/}{Dr. Kunal Agrawal} and Partner: Alex Jones, USC
\BulletItem
Description:
Implemented and augmented an order-maintenance data structure supporting \textit{O(1)} time queries and \textit{O(1)} amortized time inserts to be utilized in parallel applications for race-condition detection.  Early results indicate mere constant slowdown when on-the-fly race detection is enabled.
\end{detail}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Personal Technical Projects %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Personal
\newline Technical
\newline Projects}
{Personal Technical Projects}
{PDF:TechnicalProjects}

\textbf{Bagged and Boosted Decision Trees},
\textit{Matlab}
\begin{detail}
\BulletItem
Implemented an ID3 decision tree and utilized it in random forest and boosted tree implementations
\BulletItem
Achieved an classification accuracy of 88\% beating the professor's implementation
\end{detail}

\EntryGap
\textbf{Game Development},
\textit{C++}
\begin{detail}
\BulletItem
Designed a multi-functional game for the command line enabling users to play full implementations of Reversi, Nine Almonds, or Magic Square
\end{detail}

\EntryGap
\textbf{Topic Modeling for Classification},
\textit{Python \& NumPy}
\begin{detail}
\BulletItem
Compared implementations of latent Dirichlet allocation (LDA) and non-negative matrix factorization (NMF) in text topic modeling qualitatively
\BulletItem
Analyzed the performance of a classifier using the topics as the label space
\end{detail}

\EntryGap
\textbf{Deep Learning - Artificial Neural Networks},
\textit{Matlab}
\begin{detail}
\BulletItem
Created an artificial neural network for binary classification
\BulletItem
Utilized classic forward and backward propagation (gradient descent) algorithms for training
\end{detail}


%%%%%%%%%%%%%%%%%%%%%%
%% Technical Skills %%
%%%%%%%%%%%%%%%%%%%%%%

\section
{Technical\newline
Skills}
{Technical Skills}
{PDF:TechnicalSkills}

\textbf{Programming Languages and Software}
\par
\begin{detail}
\BulletItem
{\TeX}, {\LaTeX}, Matlab, Mathematica, R, Python, Java, Hadoop, Hive, Pig, Impala, C/C\#/C++, .NET, Cilk, Web Development, MySQL, T-SQL, Sql Server, Azure Sql, Azure Storage, Azure ML, Azure Cloud Services, and Visual Studio, 
\end{detail}

\EntryGap
\textbf{Communication}
\begin{detail}
\BulletItem
Extensive experience w/ Technical Writing and pair-programming; Excellent at public speaking and sales
\end{detail}


%%%%%%%%%%%%%%%%%%%%%%%
%% Awards and Honors %%
%%%%%%%%%%%%%%%%%%%%%%%

\section
{Awards \&\newline
Honors}
{Awards \& Honors}
{PDF:AwardsHonors}

\textbf{Yahoo! Case Competition Finalist}
\hfill
\DatestampYMD{2012}{11}{18}
\begin{detail}
\BulletItem
Chosen to present in class-wide case competition to freshman class and Google, Inc. representatives 
\BulletItem 
Proposed advertising solutions and design changes for Yahoo, Inc. utilizing user data
\end{detail}

\EntryGap
\textbf{To Write Love on Her Arms Panelist}
\hfill
\DatestampYMD{2014}{11}{15}
\begin{detail}
\BulletItem
Selected by Washington University campus organization T.W.L.O.H.A. to represent the student perspective on a panel about suicide and mental health on campus
\BulletItem
Spoke to a large audience alongside a licensed psychiatrist, a professor of anthropology, and a professor of psychology
\end{detail}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Service and Community Involvement %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section
{Community Service}
{Community Service}
{PDF:CommunityService}

\href{http://www.missionstl.org}
{\textbf{Mission St. Louis}}, Job and Leadership Training Program
\hfill
\DatestampYMD{2014}{05}{08} --
\DatestampYMD{2014}{09}{15}
\par
Mentor
\begin{detail}
\BulletItem
Guided two formerly convicted males through the process of getting their driver's license
\BulletItem
Encouraged them as they set monthly goals and aided them to achieve them
\BulletItem
Supported them through difficult times like finding a job and enduring emotional stress
\end{detail}

\EntryGap
\textbf{Computer Science Tutor}, CSE 502N
\hfill
\DatestampYMD{2015}{1}{10} --
\DatestampYMD{2015}{5}{1}
\par
Tutor and Teaching Assistant
\begin{detail}
\BulletItem
Helped struggling students with C++ programming assignments and data structure and algorithm theory
\BulletItem
Tutored students that needed extra help outside of my normal TA responsibilities
\end{detail}

%%%%%%%%%%%%%%%%
%% Activities %%
%%%%%%%%%%%%%%%%

\section
{Activities}
{Activities}
{PDF:Activities}

\href{http://reslife.wustl.edu}
{\textbf{Residential Adviser}}, Washington University Residential Life
\hfill
\DatestampYMD{2014}{08}{08} --
\DatestampYMD{2016}{05}{20}
\par
Freshman RA
\begin{detail}
\BulletItem
Trained to create and foster a community that champions diversity and inclusion.
\BulletItem
Mentored 44 freshman academically and experientially by living with them and supporting them through various academic and emotional difficulties.
\BulletItem
Coordinated numerous 300+ person events with a staff of 16.
\BulletItem
Counseled and supported students in extremely difficult situations such as experiencing suicidal ideation and being a victim of sexual violence.
\end{detail}

\EntryGap
\textbf{Cru}, Christian Campus Group
\hfill
\DatestampYMD{2012}{8}{24} --
\DatestampYMD{2016}{5}{01}
\par
Director of Discipleship
\begin{detail}
\BulletItem
Created a bible study in an attempt to create community amongst Christians in my dorm.
\BulletItem
Led other leaders in Cru to encourage them to be more proactive to underclassman, and responded to concerns about fostering new relationships.
\BulletItem
Learned the importance of considering a plurality of views and how to engage with them in meaningful ways.
\end{detail}

\EntryGap
\textbf{Strongman}
\hfill
\DatestampYMD{2015}{10}{12} -- Current
\par
Recreational Strength Athlete
\begin{detail}
\BulletItem
Compete locally in strongman competitions in which barbaric strength events result in points, and the competitor with the most points wins.
\BulletItem
1st Place, Show Me Strength Challenge, Heavyweight, 2014
\end{detail}

%%%%%%%%%%%%%%%%
%% REFERENCES %%
%%%%%%%%%%%%%%%%

%\section
%{References}
%{References}
%{PDF:References}

%\textbf{Dr. Kunal Agrawal}
%\par
%Professor of Computer Science and Engineering
%\begin{detail}
%Washington University in Saint Louis   
%\par
%Department of Computer Science and Engineering
%\par
%1 Brookings Drive, Box 1045, Saint Louis, Missouri 63105, USA
%\par
%\href{mailto:kunal@wustl.edu}
%{kunal@wustl.edu}
%\,\BulletSymbol\,
%\,(314)\,935-4838
%\end{detail}

%\EntryGap
%\textbf{Dr. Roman Garnett}
%\par
%Professor of Computer Science and Engineering
%\begin{detail}
%Washington University in Saint Louis
%\par
%Department of Computer Science and Engineering
%\par
%1 Brookings Drive, Box 1045, Saint Louis, Missouri 63105, USA
%\par
%\href{mailto:garnett@wustl.edu}
%{garnett@wustl.edu}
%\,\BulletSymbol\,
%\,(314)\,935-7302
%\end{detail}
\end{body}

%%%%%%%%%%%
% CV NOTE %
%%%%%%%%%%%

%\begin{flushright}
%\scriptsize%
%[\textit{\CVNote}]%
%\hspace{2.0mm}\null
%\end{flushright}

%\label{LastPage}~
\end{document}
